Hector Permafrost

### 2018-12-20 analysis/paper/paper.Rmd
Add some notes and references to introduction.

Permafrost carbon sink:

- [@zimov_2006_climate_change]
- [@treat_2013_permafrost_carbon_bomb]
- [@schuur_2015_climate; @schuur_2011_climate_change; @schaefer_2014_impact; @schaefer_2011_amount; @lee_2011_rate; @kuhry_2010_potential; @kessler_2017_estimating; @hope_2015_economic; @drake_2015_ancient; @burke_2017_quantifying]

@@

>>>>

Climate change is a problem (CITE: IPCC, NCA, etc.).
Important to reduce carbon emissions to meet temperature targets.
The extent of anthropogenic emissions reduction depends on what how much help (or push-back) we get from the physical and biological Earth systems.

Permafrost is an important C reservoir.
There are an estimated 500 Gt C in organic matter buried by frozen loess in the north plains of Siberia and Central Alaska [@zimov_2006_climate_change], and an additional 400 Gt C in other permafrost (CITE; see ref in Zimov), and XXX more in peat (CITE).
This frozen C can be released into the atmosphere by several processes related to warming, including aerobic respiration in thawed soil (REF) and anaeribic respiration in thermokarst lakes (REF).
These impacts are exacerbated by the fact that the Arctic is warming roughly 2.5 (???) times faster than the global average (REF).
Projections of permafrost C emissions vary.
[@schuur_2009_effect] estimate 0.8 - 1.1 Pg C yr-1.
Back-of-the-envelope estimates from [@zimov_2006_climate_change]: 10-40 g C m-3 day-1 off the bat, slowing down to equilibrium (?) rate of 0.5-5 g C m-3 day-1 for several years.

Several studies have attempted to evaluate the potential economic impacts of current and future permafrost C emissions.
@hope_2015_economic projected permafrost C emissions using the SiBCASA (TODO: write in full) land surface model and used these projections as inputs to the PAGE09 integrated assessment model (IAM).
They found that XXX.
Similarly, @gonzalez-eguino_2016_significant used the DICE (TODO: write in full) model to XXX.

(Paragraph on simple climate models.)
Hector [@hartin_2015_simple].
However, Hector does not have an explicit representation of permafrost C emissions.
In this study, we investigate whether the additional complexity and parametric and structural uncertainty of an explicit representation of permafrost may be warranted in Hector.
To do this, we evaluate the sensitivity of climate variables (as predicted by Hector) to several different exogenous scenarios of permafrost C emissions.

Some more relevant references:
- [@zimov_2006_climate_change]
- [@treat_2013_permafrost_carbon_bomb]
- [@schuur_2015_climate; @schuur_2011_climate_change; @schaefer_2014_impact; @schaefer_2011_amount; @lee_2011_rate; @kuhry_2010_potential; @kessler_2017_estimating; @hope_2015_economic; @drake_2015_ancient; @burke_2017_quantifying]

@@

Hector [@hartin_2015_simple,@hartin_2016_ocean].
Simple climate model.
